this is for the result part of the draft

### 2017-03-16 analysis/draft.Rmd
Files commited by wflow_commit.

---
title: "missing data imputation: Tumor data"
author: "wei wang"
date: 2017-03-13
output: html_document
---

@@

try the new version of the wrokflowr package

>>>>

---
title: "this is for the result part of the draft"
author: "Wei Wang"
date: 2017-03-15
output: html_document
---

@@

### data analysis on the normalized data

#### missing data imputation

#### gene expression data

### further issues

#### NMF

#### tensor flash
